%%% Use the next line if you want questions
\documentclass[12pt,addpoints]{exam}
%%% OR, use the next line if you want solutions
%\documentclass[12pt,answers,addpoints]{exam}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\sisetup{per-mode=symbol}
\usepackage{physics}
\usepackage{ifthen}
\usepackage{tikz}
\usepackage[outline]{contour} % glow around text
\usetikzlibrary{calc} % for pic
\usetikzlibrary{angles,quotes} % for pic
\usetikzlibrary{patterns}
\usepackage{ circuitikz }

\tikzset{>=latex} % for LaTeX arrow head
\contourlength{1.2pt}


\colorlet{myred}{red!65!black}
\tikzstyle{ground}=[preaction={fill,top color=black!10,bottom color=black!5,shading angle=20},
                    fill,pattern=north east lines,draw=none,minimum width=0.3,minimum height=0.6]
\tikzstyle{mass}=[line width=0.6,red!30!black,fill=red!40!black!10,rounded corners=1,
                  top color=red!40!black!20,bottom color=red!40!black!10,shading angle=20]
\tikzstyle{rope}=[brown!70!black,line width=1.2,line cap=round] %very thick

% FORCES SWITCH
\tikzstyle{force}=[->,myred,thick,line cap=round]
\tikzstyle{Fproj}=[force,myred!40]
\newcommand{\vbF}{\vb{F}}
\newboolean{showforces}
\setboolean{showforces}{true}

\pointpoints{mark}{marks}

\totalformat{Pregunta \thequestion: \totalpoints puntos}

\pointsinrightmargin
\bracketedpoints

\begin{document}

%% Some Formatting Options:
%% Make an easy blank environment (just type \blank{1.5in} now)
\newcommand\blank[1]{\makebox[#1]{\hrulefill}}
%% Tell TeX to make linebreaks before questions begin
\newcommand{\myquestion}{\filbreak\question}
\newcommand{\mypart}{\filbreak\part}
%% then replace all your \question commands with \myquestion
%% commands.  \filbreak basically means "this is a good place to break
%% the page, and fill the bottom of the page with blank space, unless you
%% can put enough more on the page to reach the next \filbreak, in which
%% case the present \filbreak will have no effect at all".  The effect of
%% \filbreak before each question is that page breaks will occur only
%% before questions.
%% This command below makes an even nicer fill-in-the-blank.
\newcommand*{\TickBox}{{\fboxsep 0pt \fbox{\rule{0em}{2em}\rule{10em}{0em}}}}

\begin{coverpages}

\begin{center}
  \begin{Large}
\vspace{-0.3in}
Swadhaa Waldorf Learning Centre

Physics Test Paper Grade 9 Ch. 1

\end{Large}
\end{center}

\vspace{0.5in}

\begin{center} \fbox{\fbox{\parbox{5.5in}{
        Grade: 9 Duration: 1 hour Subject: Physics 0625 Marks: \numpoints{}

        \bigskip

        \makebox[\textwidth]{Child's Name:\hfill}

        \bigskip
        You must answer on the question paper.

        Good luck!
        \bigskip

      }}}
  \bigskip

  INSTRUCTIONS :
  \begin{itemize}
    \item Answer all questions.
    \item Use a black or dark blue pen. You may use an HB pencil for any diagrams or graphs.
    \item Write your name in the space at the top of the page.
    \item Write your answer to each question in the space provided.
    \item Do not use an erasable pen or correction fluid.
    \item You may use calculators in this paper.
    \item You may use tracing paper.
	\item You must show all necessary working clearly.
  \end{itemize}


\end{center}

\vspace{1.1in}

\begin{center}
\begin{small}
\begingroup
  \hpword{Marks:}
  \hsword{Score:}
  \gradetable[h]
\endgroup
\end{small}
\end{center}


\end{coverpages}

\pagestyle{headandfoot} \extraheadheight{.25in}
\footer{} {Page \thepage\ of \numpages} {\iflastpage{End of exam.}{Please go on to the next page\ldots}}

\begingradingrange{mcq}
\begin{questions}
  \fullwidth{\Large \textbf{Multiple Choice Questions} \\ Marks : \pointsinrange{mcq}  }


\uplevel{No partial credit will be awarded.  Circle \emph{one} choice \emph 
for each of the multiple-choice questions.  }


\myquestion[1] The unit SI units of length, mass and time are :
\unit{\metre}, \unit{\gram}, \unit{\second}.

These are called
	\begin{choices}
	\choice Derived units
	\CorrectChoice Fundamental units.
	\choice Natural units.
	\choice Commercial units.
	\end{choices}


\myquestion[1] Which of the following quantities mesaured NOT in derived unit?

	\begin{choices}
	\correctchoice width of pencil
	\choice space occupied by a baloon
	\choice speed of a car
	\choice area of a shadow of a person
	\end{choices}


\myquestion[1] The correct unit in SI system for density $\rho$ is:

	\begin{choices}
	  \choice \unit{\kg^2\per\metre^3}
	  \choice \unit{\kg\per\centi\metre^2}
	\CorrectChoice \unit{\kg\per\m^3}
	\choice \unit{\g\per\litre^3}
	\end{choices}


\myquestion[1] The oil floats on water because ?
 \begin{choices}
   \choice Oil has less mass than water
   \correctchoice 1 \unit{\l} Water occupies less space than 1 \unit{\l} oil
   \choice 1 \unit{\l} Water occupies more space than 1 \unit{\l} oil
   \choice 1 \unit{\l} Water occupies same space as 1 \unit{\l} oil.
\end{choices}

\myquestion If mass of a boy is 32\unit{\kg} and typical density of a human body is 0.985 \unit{\g\per\cm^3}

Formula for density :  $\rho = \frac{m}{v}$ \unit{\kg\per\m^{3}}
\begin{parts}
\part[2] The density of a typical human body in \unit{\kg\per\m^3} is
	\begin{choices}
	\correctchoice 985 \unit{\kg\per\m^3}
	\choice 0.001 \unit{\kg\per\m^3}
	\choice 9.85 \unit{\kg\per\m^3}
	\choice 0.00985 \unit{\kg\per\m^3}
	\choice 0.985 \unit{\kg\per\m^3}
	\end{choices}

\part[2] Volume of the boy's body is
	\begin{choices}
	\choice 9.85 \unit{m^3}
	\correctchoice 0.03248 \unit{m^3}
	\choice 9 \unit{m^3}
	\choice 30.781 \unit{m^3}
	\choice 1 \unit{m^3}
	\end{choices}
\end{parts}

\myquestion[1] Which of the following statements is true
	\begin{choices}
	\choice Meter rule with mm markings is more accurate than Vernier caliper
	\correctchoice Vernier caliper has accuracy of 0.01 mm
	\choice Vernier caliper is used to measure accurate time
	\choice Vernier caliper is used primarily to measure road lengths
	\end{choices}


\myquestion[4] Consider following equipments


1 Meter long measuring stick

10 Meters long Measuring tape

1 Foot long student's scale


Which of the following statements are true (Mark as many as you find are true)


	\begin{choices}
	\choice 1 ft scale is more accurate than 1m rule which is more accurate than 10m measuring tape
	\correctchoice 10m measuring tape will be used to measure a shape of a room
	\choice Leaving practical difficulties aside you can measure any given length by either of these instruments
	\correctchoice The 1m rule and 1ft scale can not be used to measure lengths that are not straight lines
	\end{choices}


	\myquestion[1] A stop watch was used to measure a runner in race with following readings at start and end of the lap.

    1.	1m:40s:100ms

	2.	2m:50s:100ms

	How long did the runner take to finish the lap?

	\begin{choices}
	\choice 50.1s
	\correctchoice 50s
	\choice 90se
	\choice 110.5s
  \end{choices}

\myquestion[1] In following diagram if l = 15.5 cm


\begin{circuitikz}
\tikzstyle{every node}=[font=\LARGE]
\draw  (1.75,10.25) rectangle (10.5,9.25);
\draw  (4.25,10.75) circle (0.5cm);
\draw  (5.25,10.75) circle (0.5cm);
\draw  (6.25,10.75) circle (0.5cm);
\draw  (8.25,10.75) circle (0.5cm);
\draw  (7.25,10.75) circle (0.5cm);
\draw  (2.75,11.75) rectangle (3.75,10.25);
\draw  (8.75,11.75) rectangle (9.75,10.25);
\draw [<->, >=Stealth, dashed] (3.75,12.5) -- (8.75,12.5);
\node [font=\LARGE] at (6.5,13) {l};
\end{circuitikz}

What is the diameter of each coin?

  \begin{choices}
	\choice 310mm
	\choice 31mm
	\choice 3310mm
	\choice 3100mm
  \end{choices}





\endgradingrange{mcq}



\newpage

\begingradingrange{theory}

\fullwidth{\Large \textbf{Theory} \\ Marks : \pointsinrange{theory}}

\uplevel{For the following problems, show all your work.  Partial
marks  will be awarded for correct reasoning. Write units for all your answers. Answers without corresponding units in each step will be given zero marks. }

\question A plot of land has following dimensions:

Width = $20 ft$ and Length = $30 ft.$

\begin{parts}
	\part[1] Calculate area of the plot in $ft^{2}$ as unit.

	\begin{solutionorlines}[1in]
	\end{solutionorlines}

	\part[2] Convert the area of the plot in SI units. Hint :  $1ft = 0.305 m$
	\begin{solutionorlines}[1in]
	\end{solutionorlines}

    \part[2] If rectangular shade of height $10ft$ was erected on the entire plot. What will be the volume of the whole shade? (Ignore the thickness of the walls),

    \begin{solutionorlines}[1in]
	\end{solutionorlines}

\end{parts}

\myquestion[5] Complete the following table. e.g. SI unit of length is $m$

\begin{center}
\begin{tabular}{||c | c||}
 \hline
Quantity & SI unit  \\ [0.5ex]
 \hline\hline
 Length & $m$ \\
 \hline
 Area  &   \\
 \hline
 Time  &  \\
 \hline
 Volume  &  \\
 \hline
 Density &  \\
 \hline
  Diameter & \\
 \hline
\end{tabular}
\end{center}


\endgradingrange{theory}


\newpage

\begingradingrange{atp}

\fullwidth{\Large \textbf{Alternative to practical} \\ Marks : \pointsinrange{atp}}

\uplevel{For the following problems, show all your work.}

 Your answer must include following sections
 \begin{enumerate}
   \item Equipment required

   \item Goal of the experiment (State the reasoning for choosing this particular experiment

   \item Diagram of setup

   \item Procedure

   \item How will you determine the final result

 \end{enumerate}

Partial marks will be awarded for correct reasoning.

\question[10]
A student is given three pieces of metal. One block is of sliver. One is of Steel. Third piece is blob of unknown metal.

Design an experiment to determine if the third block is of silver or steel or neither. Hint: A block of given metal any shape and size will always have same density.

Assume that each block is made of only one metal and does not have any impurities (i.e. if it is silver it is entirely made of silver and nothing else).


\fillwithlines{\stretch{1}}

\newpage

\fillwithlines{\stretch{1}}

\endgradingrange{atp}

\newpage

\end{questions}


\end{document}
